The Development of a Programming Language

### 2022-10-30 paper.tex
final touches

\author{Florian M. Donnelly}
\title{The Development of a Programming Language}

@@

    \Large
    \vfill
    Matura Paper written by\\ \textbf{Florian M. Donnelly}

    \vspace{0.5cm}
    Under Supervision of\\ \textbf{Adrian Lüthi}

    \vspace{0.5cm}
    Gymnasium Burgdorf\\ October 31, 2022

@@

    \url{https://github.com/LeFlorians/TestScript}.

@@

    \url{https://github.com/LeFlorians/TestScript/tree/\githash}.

@@

\newpage\subsection{A Project Overview}
In the following paragraphs, the project in its entirety will be briefly
presented, giving an overview over files and correlations.

@@

\section{Declaration of Authenticity}
Hereby I, Florian M. Donnelly, declare to have written this paper independently, 
also including the entire source code of \name{}, using resources 
listed under the \emph{Bibliography} section on page \pageref{bibliography}.

>>>>

\title{The Development of a Programming Language}

@@

    \Large
    \vfill
    Matura Paper written by\\ \ver{\textbf{Florian M. Donnelly}}

    \vspace{0.5cm}
    Under Supervision of\\ \ver{\textbf{Adrian Lüthi}}

    \vspace{0.5cm}
    Gymnasium Burgdorf\ver{, 23e}\\ October 31, 2022

@@

    \ver{\url{https://github.com/LeFlorians/TestScript}.}

@@

    \ver{\url{https://github.com/LeFlorians/TestScript/tree/\githash}.}

@@

\subsection{A Project Overview}
In the following paragraphs, the project in its entirety will be briefly
presented, giving an overview over files and correlations.

@@

\section{Declaration of Authorship}
By typing my full name below, I confirm that the matura paper I am submitting is entirely
my own original work except where otherwise indicated. I am aware of the shool regulations
concerning plagiarism.

\ver{Florian Michael Donnelly}
